International Mathematical Olympiad using Plackett-Luce

### 2025-04-22 inst/imo.Rmd
better title
variable number of competitors

---
title: "imo"
author: "robin hankin"
date: "2025-04-07"
output: html_document
---

@@

>>>>

---
title: "International Mathematical Olympiad using Plackett-Luce"
author: "robin hankin"
date: "2025-04-07"
output: html_document
---

@@

# Some thoughts about including variable numbers of competitors

Above we used OECD countries for Australia to compete against.  Here I
use all the competitors:

```{r}
a <- read.table("imo.txt", header = TRUE)
min(a$year)
max(a$year)
which(subset(a,a$year == 2015)$country == "Australia")
competitors <- function(year,a){ table(a$year)[as.character(year)]   }
competitors(2013, a)
rank <- function(place, y, a){
    which(subset(a,a$year == y)$country == place)
}

rank("Australia",2001,a)
rank("Australia",2002,a)
rank("Australia",2024,a)
cbind(place = sapply(2001:2024,function(y){rank("Australia",y,a)}),
      competitors = table(a$year)
      )
```

Now try New Zealand:

```{r imo_nz}
cbind(place = sapply(2001:2024,function(y){rank("New Zealand",y,a)}),
      competitors = table(a$year)
      )
```
